%%%%%%%  STARTING HERE, Document Formatting Settings


\documentclass[a4,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
 \usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage[inline]{enumitem}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\usepackage{anyfontsize}
\usepackage[margin=1cm, top=1cm]{geometry}
\setmainfont[
BoldFont=SourceSansPro-Semibold.otf, %SourceSansPro-Bold.otf
ItalicFont=SourceSansPro-RegularIt.otf
]{SourceSansPro-Regular.otf}
\setsansfont{SourceSansPro-Semibold.otf}
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\definecolor{UI_blue}{RGB}{32, 64, 151}
\usepackage[style=nature, maxbibnames=3]{biblatex}
\addbibresource{Publications.bib}
\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-10pt} \hrulefill \vspace{-6pt}]
\newcommand{\subtext}[1]{
#1\par\vspace{-0.2cm}}
\setlist[itemize]{align=parleft,left=0pt..1em}
\newenvironment{zitemize}{
\begin{itemize}\itemsep0pt \parskip0pt \parsep1pt}
{\end{itemize}\vspace{-0.5cm}}
\newcommand{\hskills}[1]{
\textbf{\bfseries #1} }
\titleformat{\subsection}{\vspace{-0.1cm} 
\bfseries \fontsize{11pt}{2cm}}{}{0em}{}[\vspace{-0.2cm}]

%%%%%%%  END OF "Document Formatting Settings" SECTION


\begin{document}

\begin{center}
    \begin{minipage}[b]{0.24\textwidth}
            \ (+91)-9156011787 \\
            \normalsize \href{mailto:as.anandsumit@gmail.com}{as.anandsumit@gmail.com} 
    \end{minipage}% 
    \begin{minipage}[b]{0.5\textwidth}
            \centering
            {\Huge \underline {SUMIT ANAND}} \\ %
            \vspace{0.1cm}
            {\color{UI_blue} \Large{DevOps and Site Reliability Engineer}} \\
    \end{minipage}% 
    \begin{minipage}[b]{0.24\textwidth}
            \flushright \normalsize  %Willing to Relocate
            {\href{https://www.linkedin.com/in/asanandsumit/}{linkedin/asanandsumit} } \\
            \href{https://github.com/anandsumit2000}{GitHub/anandsumit2000}
    \end{minipage}   

    {\color{UI_blue} \hrulefill}
\end{center}

Site Reliability Engineer with 2 years of experience adept at developing robust monitoring tools, disaster recovery, and automation solutions. Catalyzing efficiency by transforming operations with strategic automations and ensuring high availability of systems.  %% This can be customized, but I feel this impact statement makes people want to read more.

\section{Education }

\subsection*{B.E, Computer Science Engineering} 
{{\normalsize \normalfont Cambridge Institute Of Technology - Bangalore, KA} \hfill Aug 2018 --- July 2022} 

\section{Experience}

%%%%%%% ----------------------------------- Role 5 ----------------------------------- %%%%%%%
\subsection*{Associate Software Engineer - DevOps \hfill Aug 2022 --- Present} 
\subtext{Syncron Software India Pvt. Ltd \hfill Bangalore, KA} 
    \begin{zitemize}
        \item Architected a new solution with a custom authentication layer using AWS Lambda and API Gateway on AWS Transfer Family, replacing the legacy open-source SFTP system at the service.
        \item Enhancing the CI/CD deployment method that utilizes the CDK Toolkit to empower developers to dynamically deploy changes to the data-platform(AWS Data.All) via GitHub webhooks and AWS CodePipeline.
        \item Implemented GitHub workflows to regularly scan repositories for deprecated packages, addressing vulnerabilities and potential breaches. Successfully reduced associated risks by 30\%.
        \item Upgraded EKS cluster back-ends with persistent type FSx storage volumes for resiliency and fault-tolerance. Wrote shell scripts for housekeeping the clusters for maintenance and recovery.
        \item Produced terraform scripts for provisioning resources to securely onboard businesses to the dynamic data movement platform service. Brought in automation to fetch and rotate logs from ECS fargate clusters for fault analysis. 
        \item Implemented disaster recovery plan, minimizing downtime by 90\% to enhance system resilience, guaranteeing uninterrupted service for 500+ business managers allowing them to forecast and strategize for maximum business growth. 
    \end{zitemize}


%%%%%%% ----------------------------------- Role 4 ----------------------------------- %%%%%%%
\subsection*{DevOps Engineer {\normalsize\normalfont (Intern)} \hfill Apr 2022 --- July 2022} 
\subtext{Syncron Software India Pvt. Ltd \hfill Bangalore, KA} 
    \begin{zitemize}
        \item Launched Lambda function to push Redshift Database metrics to CloudWatch, reducing issue response time by 45\%.
        \item Assisted upgrades for legacy Terraform repositories, achieving a 40\% reduction in deployment time.
    \end{zitemize}

%%%%%%% ----------------------------------- Role 3 ----------------------------------- %%%%%%%
\subsection*{DevOps and Cloud Lead \hfill Sept 2021 --- July 2022} 
\subtext{Google Developers Student Clubs - CIT Bangalore \hfill Bangalore, KA} 
    \begin{zitemize}
        \item Conducted workshops to enhance student knowledge of developer products and platforms by Google, focusing on hands-on experience with Google products. Empowered GDSC members to cultivate new skills collaboratively, growing a community learning environment to frequently engage in creating technical solutions for the communities.
    \end{zitemize}
    

%%%%%%% ----------------------------------- Role 2 ----------------------------------- %%%%%%%
\subsection*{Intern \hfill Dec 2021 --- Apr 2022} 
\subtext{Defence Research Development Organization \hfill Bangalore, KA} 
    \begin{zitemize}
        \item Streamlined recruitment processes by eliminating reliance on third-party agencies for work history verification, ensuring a more efficient and direct hiring process.
        \item Researched and implemented blockchain strategies leading to a remarkable 60\% increase in overall system efficiency and expense reduction. Additionally, successfully halved the processing time for HR transactions by leveraging a distributed network of peers sharing a ledger for employee records.
    \end{zitemize}
    
%%%%%%% ----------------------------------- Role 1 ----------------------------------- %%%%%%%
\subsection*{Developer Intern \hfill Oct 2021 --- Dec 2021} 
\subtext{R\&D, Dept. of CSE - CIT Bangalore \hfill Bangalore, KA} 
    \begin{zitemize}
        \item Focused the deployment on a Raspberry Pi using an Ubuntu server with a static Ethernet IP, enhancing system performance and stability. Incorporated Grammar and Parsing Algorithms along with the Naive Bayes algorithm into the chatbot system. 
        \item Streamlined and optimized the Raspberry Pi-based chatbot project, resulting in a 30\% reduction in admission processing time. Implemented web scraping techniques to significantly expand the question-answer database by 400\%, delivering more accurate and up-to-date information for prospective students.
    \end{zitemize}


\section{Skills}
\begin{tabular}[t] {*{10}{>{\centering\arraybackslash}p{6em}}}  
Ansible & API & AWS & Docker & Go & Google Cloud & Git & Helm & Jenkins  \\     
Kubernetes & Linux & Networks & NoSQL & Prometheus & Python & SRE & Shell & Terraform \\
\end{tabular}
\vspace{-0.2cm}

\section{Certifications}
\begin{tabular}[t]{ p{10em} p{46em}}
\hskills{Dec - 2023} & HashiCorp Certified: Terraform Associate (003) \hfill(\hskills{\href{https://www.credly.com/badges/814918e9-fc9f-4fde-8ea0-5df068b66902}{Credly} }) \\ % 
\hskills{Sept - 2023} & AWS Certified Cloud Practitioner \hfill(\hskills{\href{https://www.credly.com/badges/77765962-e64e-445f-9d74-eb272f5d6923}{Credly} })\\
\end{tabular} 

\end{document}